\documentclass{homework}
\course{Ross/Ohio 2023, General Topology}
\author{Names of Contributors}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
  The holy trinity of Topology: Interior, Boundary, and Exterior.
\end{inspiration}

\section{Terminology}

\begin{problem}
  What is a \textit{metric space}? Give as many examples of metric spaces as you can.
\end{problem}

\begin{problem}
  What is an \textit{open ball}? We write $B_r(x)$ for the open ball of radius $r$ centered at $x$.
\end{problem}

\begin{problem}
   What is an \textit{open set}? A \textit{closed set}?
\end{problem}

\begin{problem}
  Draw a set $S$. What is meant by its \textit{interior} $S^\circ$, \textit{boundary} $\partial S$, and \textit{exterior} $S^{\text{ext}}$? Draw them.

  Why is every point in exactly one of these 3 sets?
\end{problem}

\section{Computational Problems (Some food for thought)}

\begin{problem}
  We work in $\R$ with the standard metric $d(x,y)=|x-y|$.
  
  Describe the interior, boundary, and exterior of the following sets: $\emptyset$, $(0,1)$, $[0,1]$, $\Q$, $\R$.
\end{problem}

\section{Prove or Disprove and Salvage if Possible}

\begin{problem}
  An open ball $B_r(x)$ is open.
\end{problem}

\begin{problem}
  Let $\{S_i\}$ be a (possibly infinite) family of open sets. Then $\bigcup S_i$ and $\bigcap S_i$ are open.

  Does the same hold if we replace ``open" with ``closed"?
\end{problem}

\begin{problem}
  What is meant by the \textbf{closure} of a set?  Write $\bar{A}$ for the closure of $A$.
\end{problem}


\section{Exploration}

\begin{problem}
  Describe different topologies on the set $\{ 0, 1 \}$.
\end{problem}

\section{Prove or Disprove and Salvage if Possible}

\begin{problem}
  The set $X$ is open if and only if $\int X = X$.
\end{problem}


\end{document}
